Generate data for multispecies modeling, including diet!

### 2020-10-05 NOBAmsdiets.Rmd
start reading in multiple surveys with names WIP

#### Biomass index
```{r bioind-1, eval=FALSE}

omlist_ss <- NOBAom_ms
source(here("config/omdimensions.R"))

@@

survObsBiom <- NOBAom_ms_ind$survObsBiom

@@

# problem--omdimensions is doing species age accounting wrong
# species alphabetical pulled separately but ages not
# pull species name, n age classes and n ages all at once to avoid bad sorting
```

@@

#### Catch time series
```{r catchind-1, eval=FALSE}
#read time series data
catchbio_ss <- readRDS(file.path(d.name, paste0(scenario.name, "fishCatch.rds")))

>>>>

#### Biomass index
```{r bioind-1}

omlist_ss <- readRDS(file.path(d.name, paste0(scenario.name, "omlist_ss.rds")))
source(here("config/omdimensions.R"))

@@

# object in memory is no longer the same as saved files, need to read back into same configuration
# list of files in directory with surveyB.rds ending
# append to survObsBiom
survs <- list.files(path=d.name, pattern = "*surveyB.rds", full.names = TRUE)
survey.name <-  
survObsBiom <- lapply(survs, readRDS)

#survObsBiom <- NOBAom_ms_ind$survObsBiom

# survey.name="BTS_fall_allbox_effic1"
# fallsurv <- readRDS(file.path(d.name, paste0(scenario.name, "_",survey.name,"surveyB.rds")))

@@

# problem--omdimensions is doing species age accounting wrong
# species alphabetical pulled separately but ages not
# pull species name, n age classes and n ages all at once to avoid bad sorting
# also fix same problem in om_index with wtatage hack!
```

@@

#### Catch time series
```{r catchind-1}
#read time series data
catchbio_ss <- readRDS(file.path(d.name, paste0(scenario.name, "fishCatch.rds")))
